\section{Further Work}
Through this project we have been looking at what can be found in cleartext in 
the memory of android phones to get an idea of how the volatile memory in 
android devices  can be useful. Based on our findings we can say that there are
valuable information in the memory that can become relevant in a forensics investigation. 
From this there are a number of areas that can be researched.

The first and most critical area to make this valuable would be looking into how 
to actually get the memory of a live device, using the technique we have with 
the emulator, in most cases require a "cold" reboot of the device risking degrading 
the volatile memory.

Another topic for further work would be in developing tools to look through the 
memory data automatically, as in most cases you don't know exactly what you will 
be looking for some looking for some sort of pattern to find data consistently. 
This gets increasingly important as the memory capacity in these devices is increasing 
quickly. The leap from our emulated device with 800MB memmory to newer devices 
with 2GB and higher capacity would make it not feasible to go through the data manually.

The fact that our research into secure applications isn't entirely conclusive, we
couldn't find the encryption  key or any messages sent or received using this 
secure application, but they key is most likely in the memory. How 
securely hashed or stored this is might be despite the fact its not in clear text 
isn't currently known. Using a different technique and a deeper search might 
reveal different results.

Lastly, and this is a topic we intended to research further in our own paper is 
how long different sorts of information stays in memory. This is probably 
something that will be hard to test using an emulator as actual live devices will 
have a lot more apps and background services running. And you won't be likely to 
get as clean a memory as we did with our experiments with the emulator. 

In this paper we have only looked Android running with the Dalvik virtual machine, 
in the more recent versions of Android the experimental Android RunTime(ART) 
virtual machine is introduced. This changes how apps are compiled and run, from 
Dalviks just-in-time memory management to ART’s ahead-of-time management. We 
believe this might impact how memory is managed, and might cause different 
results to the ones presented in this paper and might be a topic for further research. \\