\section{Related Work}
In the last years there has been done a lot of research on acquisition of memory
and analysis techniques, targeting Linux and Android. The most common way to 
gain access to memory is gaining root privileges and loads a new kernel into the 
phone. While this is not ideal, as it is overwriting some of the memory in the 
progress, it is the only known way to get access to memory of all running processes.\\

In 2011 J. Sylve et al. presented a paper that described a forensic sound 
approach of acquiring Android memory. \cite{acq_vol_android_mem} This paper looked 
into ways of obtaining memory, with different tools and different approaches. The paper 
tries different ways to acquire memory and by using a feature(pmemsave) in the emulator. 
This creates a perfect snapshot of the memory and could compare memory dumps from other 
tools and see how much they differed from the first. When compared to another method 
called Droid Memory Dumpstr (DMD) it was over 99\% identical. Since the memory dumps 
takes time, in our experiment it took us 5 minutes to dump 800mb of memory, some 
changes will naturally occur in the memory.\\

Based on these results, the paper presents a method for dumping memory that is a 
forensic sound process and can be used as evidence in court. To analyze the memory 
acquired, different methods can be used, this paper also used Volatility.
One of the key benefits of Volatility is the ability to make your 
own plugins. The paper presents a new plugin that finds the regions where in memory 
each process is mapped, to make it easier to manually analyze it. Unfortunately we were not 
able to find this plugin to test it.\\
% Hvem er they? Var det ikke disse pluginsa vi testa?

Their paper may be the first paper published that presents a method of accurate memory acquisition on
Android, as they write in their conclusions "To our knowledge, this is the first published work on
accurate physical memory acquisition and deep memory analysis of the Android kernel's structures"\\

In 2012 a paper called Forensic Recovery of Scrambled Telephones (FROST) was 
released, in this paper it was presented a tool for forensic recovery of 
scrambled android phones. With this tool it made it possible to retrieve disk 
encryption keys from the volatile memory.\cite{frost_paper}\\

To perform this kind of attack you must place the phone in a cold place like a 
freezer, so the phone itself goes below 10 degree celsius. In their experiment 
they place a phone in a -15 degree freezer for 60 minutes. They then reset the 
phone, either with a dedicated reset-button (if the phone has one) or quickly 
taking the battery in and out to make it reset. These procedures are very time 
sensitive, so it’s very important that they are performed precise and fast. 
Next step is pressing the volume up, down and power button at the same time to 
make the phone jump into “fastboot mode”. From there it’s possible to load the 
FROST recovery image and boot that up.\footnote{http://www1.cs.fau.de/frost/}
